\assignment

### 2017-03-22 project/paper.rnw
Made progress on the presentation.

\subsection{Simple UXO Site}

<<uxoexampledata>>=
# Path to my writing project root directory.
vspuxo <- file.path('..', '..', 'vspuxo')

# Load my functions for working with UXO data.
source(file.path(vspuxo, 'rfns', 'data_functions.r'))
source(file.path(vspuxo, 'rfns', 'sampling_functions.r'))
source(file.path(vspuxo, 'rfns', 'spatial_functions.r'))

# Define the window for the UXO site.
site_window <- owin(poly = cbind(x = c(1564294, 1564495, 1556870, 1557126),
                                 y = c(535421, 541130, 541085, 535576)))
@

@@

<<truth, cache = TRUE, fig.width = 4, fig.pos = 't', fig.cap = 'True intensity at the simulated UXO site.'>>=
# Create an image of the surface in 20 ft by 20 ft pixels.
# The gauss.elliptic function from spatial_functions.r is a bivariate normal
# intensity parameterized in terms of the center, major and minor axis scales,
# and angle of the major axis.
x <- seq(1556880, 1564495, by = 20)
y <- seq(535431, 541130, by = 20)
intense.mat <- matrix(100, nrow = length(x), length(y))
for(i in seq_along(x)){
  for(j in seq_along(y)){
    intense.mat[i, j] <- 100 + gauss.elliptic(x[i], y[j],
        mu.x = 1558400, mu.y = 540000,
        s.a = 800 / (2 * qnorm(0.995)), s.b = 1200 / (2 * qnorm(0.995)),
        r = pi/6, maxrate = 200
      ) + gauss.elliptic(x[i], y[j],
        mu.x = 1562000, mu.y = 537000,
        s.a = 2000 / (2 * qnorm(0.995)), s.b = 900 / (2 * qnorm(0.995)),
        r = 0, maxrate = 200
      )
  }
}
intense.im <- im(t(intense.mat), x, y, unitname = c('foot', 'feet'))

par(mar = c(0, 0, 1, 3))
plot(intense.im, main = 'True Intensity Surface',
     border = NA, zlim = c(100, 300), las = 2)
plot(setminus.owin(owin(c(1556870, 1564495), c(535421, 541130)),
     site_window), col = 'white', border = 'white', lwd = 2, add = TRUE)
mtext('Anomalies per Acre', 4, line = 2)
@

<<sim2000obs, fig.pos = 't', fig.cap = 'Observed geomagnetic anomalies from one realization of the UXO site. The transects are not shown on this plot because they would obscure the points.'>>=
# Load the sample data used in my writing project.
# The anomaly file contains the locations of the observed anamolies and the
# cog file contains the course-over-ground waypoints on the transects.
ex_anom <- read.csv(file.path(vspuxo, 'datasets', 'easy', 'sample',
                    'easy_sample_tTA2_p200_bg100_fg200_rep2000.anomaly'))
ex_path <- read.csv(file.path(vspuxo, 'datasets', 'easy', 'sample',
                    'easy_sample_tTA2_p200_bg100_fg200_rep2000.cog'))

# Create a spatstat window and ppp object.
ex_win <- intersect.owin(site_window,
  do.call(union.owin, lapply(unique(ex_path$x), function(x){
    return(owin(c(x - 3, x + 3), c(535421, 541130)))
  })))
ex_ppp <- ppp(ex_anom$x, ex_anom$y, window = ex_win)

@@

<<polyfit1, eval = FALSE>>=
ex_fit4 <- ppm(ex_ppp ~ polynom(x, y, 4))
@

\section{Simulation Study}

What to compare? MSPE for this method vs the moving average kriging? I'd
like to cross-validate (could leave one transect out) but I don't know how to
contruct a criterion. Maybe compare modeled intensity within the rectangle to
a kernel intensity estimate?

>>>>

\section{Simulated UXO Site}

<<uxoexampledata>>=
# Define the window for the UXO site.
site_window <- owin(poly = cbind(x = c(1564294, 1564495, 1556870, 1557126),
                                 y = c(535421, 541130, 541085, 535576)),
                    unitname = c('foot', 'feet'))
@

@@

<<truth, cache = TRUE, fig.width = 4, fig.pos = 't', fig.cap = 'True intensity at the simulated UXO site.'>>=
# Bivariate normal intensity function that I originalally wrote for my
# writing project, parameterized in terms of the major and minor axes scales
# and the angle of the major axis from horizontal.
#   a is horizontal axis, b is vertical axis, r is rotation angle
gauss.elliptic <- function(x, y, mu.x = 0, mu.y = 0, s.a = 1, s.b = 1,
                           r = 0, maxrate = 1){
  rot <- zapsmall(matrix(c(cos(r), sin(r), -sin(r), cos(r)), nrow = 2))
  ab <- diag(c(s.a^2, s.b^2))
  sigma <- rot %*% ab %*% t(rot)
  siginv <- solve(sigma)
  mu <- matrix(c(mu.x, mu.y), nrow = 2)
  mat <- matrix(rbind(x, y), nrow = 2)
  return(maxrate * apply(mat, 2, function(vec){
      exp(-t(vec - mu) %*% siginv %*% (vec - mu) / 2)
    }))
}

# Create an image of the surface in 20 ft by 20 ft pixels.
x <- seq(1556880, 1564495, by = 20)
y <- seq(535431, 541130, by = 20)
intense.mat <- matrix(100, nrow = length(x), length(y))
for(i in seq_along(x)){
  for(j in seq_along(y)){
    intense.mat[i, j] <- 100 + gauss.elliptic(x[i], y[j],
        mu.x = 1558400, mu.y = 540000,
        s.a = 800 / (2 * qnorm(0.995)), s.b = 1200 / (2 * qnorm(0.995)),
        r = pi/6, maxrate = 200
      ) + gauss.elliptic(x[i], y[j],
        mu.x = 1562000, mu.y = 537000,
        s.a = 2000 / (2 * qnorm(0.995)), s.b = 900 / (2 * qnorm(0.995)),
        r = 0, maxrate = 200
      )
  }
}
intense.im <- im(t(intense.mat), x, y, unitname = c('foot', 'feet'))

par(mar = c(0, 0, 1, 3))
plot(intense.im, main = 'True Intensity Surface',
     border = NA, zlim = c(100, 300), las = 2)
plot(setminus.owin(owin(c(1556870, 1564495), c(535421, 541130),
                        unitname = c('foot', 'feet')),
     site_window), col = 'white', border = 'white', lwd = 2, add = TRUE)
mtext('Anomalies per Acre', 4, line = 2)
@

<<sim2000obs, fig.pos = 't', fig.cap = 'Observed geomagnetic anomalies from one realization of the UXO site. The transects are not shown on this plot because they would obscure the points.'>>=
# Load the sample data used in my writing project.
# The anomaly file contains the locations of the observed anamolies and the
# cog file contains the course-over-ground waypoints on the transects.
ex_anom <- read.csv('easy_sample_tTA2_p200_bg100_fg200_rep2000.anomaly')
ex_path <- read.csv('easy_sample_tTA2_p200_bg100_fg200_rep2000.cog')

# Create a spatstat window and ppp object.
ex_win <- intersect.owin(site_window,
  do.call(union.owin, lapply(unique(ex_path$x), function(x){
    return(owin(c(x - 3, x + 3), c(535421, 541130),
           unitname = c('foot', 'feet')))
  })))
ex_ppp <- ppp(ex_anom$x, ex_anom$y, window = ex_win)

# Create a ppp object the uses the full region as the window.
ex_ppp_full <- ppp(ex_anom$x, ex_anom$y, window = site_window)

@@

<<polyfit1, warning = FALSE, fig.width = 6, fig.height = 8, fig.pos = 'p', fig.cap = ''>>=
# Create a quadrature scheme manually to ensure there are dummy points on
# each transect.
# TODO: Figure out weights.
ex_Q <- quad(data = ex_ppp,
             dummy = as.ppp(rbind(
               data.frame(vertices(Window(ex_ppp))),
               do.call(rbind, lapply(unique(ex_path$x), function(x){
                 return(data.frame(
                   x = x, y = seq(min(ex_path$y), max(ex_path$y),
                                  length.out = 128)
                 ))}))), W = Window(ex_ppp)))

ex_fit2 <- ppm(ex_Q, ~ polynom(scale(x, center = 1556870, scale = 7625),
                               scale(y, center = 535421, scale = 5709),
                                     2), correction = 'iso')
ex_fit3 <- ppm(ex_Q, ~ polynom(scale(x, center = 1556870, scale = 7625),
                               scale(y, center = 535421, scale = 5709),
                                     3), correction = 'iso')
ex_fit4 <- ppm(ex_Q, ~ polynom(scale(x, center = 1556870, scale = 7625),
                               scale(y, center = 535421, scale = 5709),
                                     4), correction = 'iso')
ex_fit5 <- ppm(ex_Q, ~ polynom(scale(x, center = 1556870, scale = 7625),
                               scale(y, center = 535421, scale = 5709),
                                     5), correction = 'iso')
ex_fit6 <- ppm(ex_Q, ~ polynom(scale(x, center = 1556870, scale = 7625),
                               scale(y, center = 535421, scale = 5709),
                                     6), correction = 'iso')
ex_fit7 <- ppm(ex_Q, ~ polynom(scale(x, center = 1556870, scale = 7625),
                               scale(y, center = 535421, scale = 5709),
                                     7), correction = 'iso')
ex_fit8 <- ppm(ex_Q, ~ polynom(scale(x, center = 1556870, scale = 7625),
                               scale(y, center = 535421, scale = 5709),
                                     8), correction = 'iso')
ex_fit9 <- ppm(ex_Q, ~ polynom(scale(x, center = 1556870, scale = 7625),
                               scale(y, center = 535421, scale = 5709),
                                     9), correction = 'iso')
ex_fit10 <- ppm(ex_Q, ~ polynom(scale(x, center = 1556870, scale = 7625),
                                scale(y, center = 535421, scale = 5709),
                                      10), correction = 'iso')
ex_fit11 <- ppm(ex_Q, ~ polynom(scale(x, center = 1556870, scale = 7625),
                                scale(y, center = 535421, scale = 5709),
                                      11), correction = 'iso')
ex_fit12 <- ppm(ex_Q, ~ polynom(scale(x, center = 1556870, scale = 7625),
                                scale(y, center = 535421, scale = 5709),
                                      12), correction = 'iso')

par(mfrow = c(4, 3), mar = c(1, 0, 1.2, 3), las = 2, cex = 1)

# Multiply predictions by 43560 to convert from anomalies per square foot
# to anomalies per acre.
plot(43560 * predict(ex_fit2, window = site_window), main = '2nd Degree')
plot(43560 * predict(ex_fit3, window = site_window), main = '3rd Degree')
plot(43560 * predict(ex_fit4, window = site_window), main = '4th Degree')
plot(43560 * predict(ex_fit5, window = site_window), main = '5th Degree')
plot(43560 * predict(ex_fit6, window = site_window), main = '6th Degree')
plot(43560 * predict(ex_fit7, window = site_window), main = '7th Degree')
plot(43560 * predict(ex_fit8, window = site_window), main = '8th Degree')
plot(43560 * predict(ex_fit9, window = site_window), main = '9th Degree')
plot(43560 * predict(ex_fit10, window = site_window), main = '10th Degree')
plot(43560 * predict(ex_fit11, window = site_window), main = '11th Degree')
plot(43560 * predict(ex_fit12, window = site_window), main = '12th Degree')
plot(43560 * density(ex_ppp_full) * area(ex_ppp_full) / ex_ppp_full$n,
     main = 'Kernel Density')
@

\texttt{plot} doesn't work, and \texttt{predict} doesn't work on the original
window. \texttt{predict} can't compute SEs.
